Watch Out for the Bully! Job Interference Study on Dragonfly Network

### 2016-04-04 methodology.tex
one other todo in methodology

The parameters for building the dragonfly network studied in our work are informed by the model proposed by Kim et al.~\cite{kim-micro}. Our dragonfly network consists of 33 groups, each containing eight routers. Each router has four compute nodes attached to it. Overall, there are 264 routers and 1056 compute nodes in the network. \TODO{What's the resulting router radix?} The aggregate bandwidth of the terminal links, as well as the local and global channels, are proportional to those of the Cray Cascade system~\cite{faanes} \TODO{What are these bandwidths?}. In this work, we simulate the network performance and job interference across six different job placement and routing policy combinations, which are summarized in Table~\ref{tab: placement routing configs}.

>>>>

The parameters for building the dragonfly network studied in our work are informed by the model proposed by Kim et al.~\cite{kim-micro}. Our dragonfly network consists of 33 groups, each containing eight routers. Each router has four compute nodes attached to it. Overall, there are 264 routers and 1056 compute nodes in the network. \TODO{What's the resulting router radix? What's the classic $a,h,p$ (or whatever they are :) parameters?} The aggregate bandwidth of the terminal links, as well as the local and global channels, are proportional to those of the Cray Cascade system~\cite{faanes} \TODO{What are these bandwidths?}. In this work, we simulate the network performance and job interference across six different job placement and routing policy combinations, which are summarized in Table~\ref{tab: placement routing configs}.
